visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2023-10-17 appendix_2.Rmd
making figures

## MGCFA Model Fit Statistics

Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals). These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.

```{r tab1, results='asis'}
apa_table(results.invariant$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Invariant Model")
```

```{r tab2, results='asis'}
apa_table(results.small.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Loadings")
```

```{r tab3, results='asis'}
apa_table(results.med.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Loadings")
```

```{r tab4, results='asis'}
apa_table(results.large.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Loadings")
```

```{r tab5, results='asis'}
apa_table(results.small.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Intercepts")
```

```{r tab6, results='asis'}
apa_table(results.med.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Intercepts")
```

```{r tab7, results='asis'}
apa_table(results.large.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Intercepts")
```

```{r tab8, results='asis'}
apa_table(results.small.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Residuals")
```

```{r tab9, results='asis'}
apa_table(results.med.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Residuals")
```

```{r tab10, results='asis'}
apa_table(results.large.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Residuals")
```

>>>>

# MGCFA Model Fit Statistics

Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each loadings, intercepts, and residuals). These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb [@cheung2002], such as $\Delta$ CFI or $\Delta$ RMSEA, to the visualizations presented in the manuscript.

```{r tab1, results='asis'}
apa_table(results.invariant$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Invariant Model")
```

```{r tab2, results='asis'}
apa_table(results.small.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Loadings")
```

```{r tab3, results='asis'}
apa_table(results.med.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Loadings")
```

```{r tab4, results='asis'}
apa_table(results.large.load$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Loadings")
```

```{r tab5, results='asis'}
apa_table(results.small.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Intercepts")
```

```{r tab6, results='asis'}
apa_table(results.med.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Intercepts")
```

```{r tab7, results='asis'}
apa_table(results.large.int$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)),
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Intercepts")
```

```{r tab8, results='asis'}
apa_table(results.small.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Residuals")
```

```{r tab9, results='asis'}
apa_table(results.med.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Residuals")
```

```{r tab10, results='asis'}
apa_table(results.large.res$model_fit %>% 
            dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
            mutate(model = tools::toTitleCase(model)), 
          digits = 3, 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Residuals")
```

### 2023-10-17 manuscript.Rmd
making figures

# devtools::install_github("psyteachr/introdataviz")
# devtools::install_github("ddueber/dmacs")
# devtools::install_github("doomlab/visualizemi")
library(introdataviz)
library(dmacs)
library(visualizemi)

@@

The output from this function are several *ggplot2* objects that can be edited or saved directly using *ggplot2* functionality [@R-ggplot2].

@@

```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
invariant.plot$complete
```

@@

```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
plot_mi(
  data_coef = results.small.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.small.load$model_configural, # what model results do you want 
  lv_name = "lv"
)$complete
```

```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
plot_mi(
  data_coef = results.med.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.med.load$model_configural, # what model results do you want 
  lv_name = "lv"
)$complete
```

```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
plot_mi(
  data_coef = results.large.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.large.load$model_configural, # what model results do you want 
  lv_name = "lv"
)$complete
```

@@

```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
plot_mi(
  data_coef = results.small.int$model_coef, # output from model_coef
  model_step = "loadings", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.small.int$invariance_models$model.loadings, # what model results do you want 
  lv_name = "lv"
)$complete
```

```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
plot_mi(
  data_coef = results.med.int$model_coef, # output from model_coef
  model_step = "loadings", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.med.int$invariance_models$model.loadings, # what model results do you want 
  lv_name = "lv"
)$complete
```

```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
plot_mi(
  data_coef = results.large.int$model_coef, # output from model_coef
  model_step = "loadings", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.large.int$invariance_models$model.loadings, # what model results do you want 
  lv_name = "lv"
)$complete
```

@@

```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
plot_mi(
  data_coef = results.small.res$model_coef, # output from model_coef
  model_step = "intercepts", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.small.res$invariance_models$model.intercepts, # what model results do you want 
  lv_name = "lv"
)$complete
```

```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
plot_mi(
  data_coef = results.med.res$model_coef, # output from model_coef
  model_step = "intercepts", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.med.res$invariance_models$model.intercepts, # what model results do you want 
  lv_name = "lv"
)$complete
```

```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
plot_mi(
  data_coef = results.large.res$model_coef, # output from model_coef
  model_step = "intercepts", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.large.res$invariance_models$model.intercepts, # what model results do you want 
  lv_name = "lv"
)$complete
```

@@

1) `saved_configural`: a saved fitted model at the configural level with no equality constraints. This model should include all other *lavaan* settings you would like to use, such as `estimator` or `ordered`.

@@

means_invariant <- boot_rr_DF %>% filter(type == "Invariant") %>% group_by(model) %>% summarize(mean_h = mean(h_nmi_p))
```

@@

```{r invariance-partial-fig, include = T, fig.cap = "Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data."}
boot.partial.invariant$invariance_plot
```

```{r density-partial-fig, include = T, fig.cap = "Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision."}
suppressMessages(boot.partial.invariant$density_plot)
```

```{r effect-partial-fig, include = T, fig.cap = "Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data. The size of the dots indicate the number of data points for that estimate."}
boot.partial.invariant$effect_invariance_plot
```

@@

suppressWarnings(effect_invariance_plot)
```

@@

suppressMessages(density_plot)
```

@@

```{r rs-table, results = 'asis'}
apa_table(results.rs$model_fit %>% 
        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
        digits = 3, 
        col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for RS-14 Example")
```

@@

By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points. Generally, students show higher means on the items of the RS14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts. Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale. Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com. The effect size from $d_{MACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7])`. In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`). See Figure \@ref(fig:rs7-img) for the difference between item intercepts and latent means.

@@

```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 Item Invariance Visualization"}
# plot the image for RS7
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS7", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete
```

@@

```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 Item Invariance Visualization"}
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS6", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS6), max(DF$RS6)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete
```

@@

```{r table-boot-effects, results='asis'}
apa_table(boot.partial.rs$boot_effects,
          digits = 3, 
          caption = "Boot Partial Effects Results for RS-14 Intercepts")
```

```{r rs-partial-pic, include = T, fig.cap="RS14 scale invariance for item intercepts. The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance."}

plot_grid(
  boot.partial.rs$invariance_plot,
  boot.partial.rs$effect_invariance_plot)
```

```{r rs-partial-pic2, include = T, fig.cap = "RS14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter."}
suppressMessages((boot.partial.rs$density_plot))
```

>>>>

# devtools::install_github("psyteachr/introdataviz")
# devtools::install_github("ddueber/dmacs")
# devtools::install_github("doomlab/visualizemi")
library(introdataviz)
library(dmacs)
library(visualizemi)
library(patchwork)

@@

The outputs from this function are several *ggplot2* objects that can be edited or saved directly using *ggplot2* functionality [@R-ggplot2].

@@

```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
invariant.plot$complete

ggsave("figures/invariant-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
plot_mi(
  data_coef = results.small.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.small.load$model_configural, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/small-load-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
plot_mi(
  data_coef = results.med.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.med.load$model_configural, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/med-load-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
plot_mi(
  data_coef = results.large.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.large.load$model_configural, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/large-load-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
plot_mi(
  data_coef = results.small.int$model_coef, # output from model_coef
  model_step = "loadings", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.small.int$invariance_models$model.loadings, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/small-int-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
plot_mi(
  data_coef = results.med.int$model_coef, # output from model_coef
  model_step = "loadings", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.med.int$invariance_models$model.loadings, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/med-int-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
plot_mi(
  data_coef = results.large.int$model_coef, # output from model_coef
  model_step = "loadings", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.large.int$invariance_models$model.loadings, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/large-int-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
plot_mi(
  data_coef = results.small.res$model_coef, # output from model_coef
  model_step = "intercepts", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.small.res$invariance_models$model.intercepts, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/small-res-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
plot_mi(
  data_coef = results.med.res$model_coef, # output from model_coef
  model_step = "intercepts", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.med.res$invariance_models$model.intercepts, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/med-res-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
plot_mi(
  data_coef = results.large.res$model_coef, # output from model_coef
  model_step = "intercepts", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
  conf.level = .95, # what ci do you want
  model_results = results.large.res$invariance_models$model.intercepts, # what model results do you want 
  lv_name = "lv"
)$complete

ggsave("figures/large-res-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

1) `saved_configural`: a saved fitted model at the configural level with no equality constraints. This model should include all other lavaan settings you would like to use, such as estimator or ordered.
2) `data`: The dataframe where the model was estimated. 
3) `model`: The model syntax for the overall model.
4) `group`: The grouping variable column in the dataframe. 
5) `nboot`: The number of bootstraps to run. 
6) `invariance_index`: The fit index you would like to use to determine invariance. Please use options and labeling from *lavaan* - see `fitmeasures()` for options. 
7) `invariance_rule`: The invariance difference score you would like to use as your rule. 
8) `group.equal`: The equality constraints including in your original multi-group tests.

@@

means_invariant <- boot_rr_DF %>% filter(type == "Invariant") %>% group_by(model) %>% summarize(mean_h = mean(h_nmi_p))

ggsave("figures/prop-boot-rr.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r invariance-partial-fig, include = T, fig.cap = "Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data."}
boot.partial.invariant$invariance_plot

ggsave("figures/boot-partial-invariance.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r density-partial-fig, include = T, fig.cap = "Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision."}
suppressMessages(boot.partial.invariant$density_plot)

ggsave("figures/boot-partial-density.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r effect-partial-fig, include = T, fig.cap = "Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data. The size of the dots indicate the number of data points for that estimate."}
boot.partial.invariant$effect_invariance_plot

ggsave("figures/boot-partial-effects.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

suppressWarnings(effect_invariance_plot)

ggsave("figures/partial-large-loading-effect.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

suppressMessages(density_plot)

ggsave("figures/partial-large-loading-density.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r rs-table, results = 'asis'}
apa_table(results.rs$model_fit %>% 
        dplyr::select(model, AIC, BIC, cfi, tli, rmsea, srmr) %>% 
          mutate(model = tools::toTitleCase(model)), 
        digits = 3, 
        col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for RS-14 Example")
```

@@

By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points. Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts. Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale. Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com. The effect size from $d_{MACS}$ suggests a small to medium effect, `r apa_num(lavaan_dmacs(partial.rs.1$invariance_models$model.intercepts, "Clinical")$DMACS[7])`. In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our $\Delta$CFI criterion (i.e., \<= .01 downward change in fit: metric CFI = `r apa_p(results.rs$model_fit$cfi[5])`, partial scalar CFI = `r apa_p(partial.rs.1$model_fit$cfi[6])`). See Figure \@ref(fig:rs7-img) for the difference between item intercepts and latent means.

@@

```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 Item Invariance Visualization"}
# plot the image for RS7
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS7", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete

ggsave("figures/rs7-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 Item Invariance Visualization"}
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS6", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS6), max(DF$RS6)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete

ggsave("figures/rs6-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r table-boot-effects, results='asis'}
apa_table(boot.partial.rs$boot_effects %>% 
            dplyr::select(term, non_invariant, random_non_invariant, h_nmi, h_nmi_p) %>% 
            mutate(term = gsub("~1", " Intercept", term)),
          col.names = c("Term", "Non-Invariant", "Random Non-Invariant", 
                        "$h_{nmi}$", "$h_{nmi_p}$"),
          escape = F,
          digits = 3, 
          caption = "Boot Partial Effects Results for RS-14 Intercepts")
```

```{r rs-partial-pic, include = T, fig.cap="RS-14 scale invariance for item intercepts. The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance."}

legend_all <- get_legend(boot.partial.rs$effect_invariance_plot +
                           theme(legend.direction = "horizontal",
                                 legend.justification="center",
                                 legend.box.just = "bottom"))

(boot.partial.rs$invariance_plot + theme(legend.position = "none") + boot.partial.rs$effect_invariance_plot + theme(legend.position = "none")) /  
  legend_all

ggsave("figures/rs-boot-partial.png", dpi = 300, 
       width = 8, 
       units = "in")
```

```{r rs-partial-pic2, include = T, fig.cap = "RS-14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter."}
suppressMessages((boot.partial.rs$density_plot))

ggsave("figures/rs-boot-density.png", dpi = 300, 
       width = 8, 
       units = "in")
```
